---
title: "ReadMe"
author: "Mark"
date: "14/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Shiny Basics

### 01_data_prep
Reads in initial data set and splits up this data set into 3 files
These files are then saved in the directory "neiss"

The file `data_analysis.r` just has a look at the data sets in neiss and does
some exploratory stuff.

### 02_basics_reactive
The file `prototype.r` contains a good example of using a reactive function

code snippet here:

```{r eval = FALSE}
# injuries loaded previously
# the value of selcted will change each time input$code changes
selected <- reactive(injuries %>% filter(prod_code == input$code))
# and then this how to use
selected() %>% count(diag, wt = weight, sort = TRUE)
```

This also uses the ui components:

`fluidRow(column(8, ui_component, 4, ui_component))`

The file `polish-tables 2.r` has some great snippets of parameterising 
dplyr using the {} syntax. 

The file `polish-tables.R` has a data.frame called selected which is made to
be a reactive object and is tied to the user chaning an input box.  This 
'selected' data.frame is then used in a subsequent reactive expression which 
generates a data.frame called summary.  This summary() object is reactive then 
used to create a graph.   

The file `narrative.R` shows how to connect an action button and pull
out and display a piece of text. 

### 03_more_advanced
The file `app 4.r` shows how to capture clicks on a graph and show the 
cordinates that were clicked.

The file `app_2.r` shows a row of a data frame when the user clicks exactly
on a point in the graph. 

The file `app2_doggie.r` shows how to display a photo jpg which is stored
on disk. It also shows the glue package which in this case enables a variable
to be inserted into a piece of html.

The file `app.r` show us the **observeEvent()** function which monitors an input
widgit (in this case a click from a button.). This also shows the 
**showNotification("So long", duration = 3, type = "error")** function which 
prints message to screen.



## Plotly

## 04_plotly_fundermentals

### Plotly_01_basics
The following are in `plotly_01_basics.R`

* Convert a basic ggplot into a scatter plot
* Create a basic plot.ly bar chart [reorder factor]
* Create a histogram 
* bivariate graphics - scatter plot and stacked bar chart


### Plotly_02_colors_opacity_glyphs_hover

The following are in `plotly_02_colors_opacity_glyphs_hover.R`

* Specify color
* Specify opacity - because of overplotting
* Change glyph
* Add specific colour
* Map scatter points to various colors
* Add a theme eg "dark2" for colours
* Define specific colours as a vector
* Hover information for scatter plots

### Customising your layout 

See `plotly_03_customising_layout.R`

# Adding axis labels
# transform scale --- log scale......
# remove zero line
# customise the canvas


## 05_plotly_beyond_basics

### Layering
See `plotly_04_layering.R`

* Layering traces ---- adding loess to a scatter plot
* Compare two models 1 scatter plot and 2 lines 
* layering densities === these are like histograms === only with lines.


### Subplots facets 

Subplots correlation matrices and heatmaps (2d histograms).

See here `plotly_05_subplots_and_facets.R` 

* Subplot - These are like facets
* automatically creating facets   group_by() + do()
* scatterplot matrices (pair wise ) (note lassoo selection - interactive )
* binned scatter plot [heatmap] 


### D3 Examples
See here `d3_markdown`

## To do
* d3 work through r2d3 examples here: https://rstudio.github.io/r2d3/articles/introduction.html
* d3 user control
* r markdown css        DONE
* r markdown sass       DONE
* fonts in markdown
* flexdashboards
* programmatically build R markdown
* parameterise R markdown
* download gitlab
* data.table rewrite
* r arrow
* r studio theme
* dyson

include fragments of html https://bookdown.org/yihui/rmarkdown-cookbook/include-html.html




## Links
https://unleash-shiny.rinterface.com/index.html
https://engineering-shiny.org/
https://happygitwithr.com/
https://shiny.rstudio.com/articles/layout-guide.html
https://shiny.rstudio.com/articles/modules.html
https://shiny.rstudio.com/articles/css.html
https://bootswatch.com/
https://adv-r.hadley.nz/functionals.html
Shiny Cheetsheet
https://www.aridhia.com/blog/using-shiny-modules-to-simplify-building-complex-apps/
https://emilyriederer.netlify.app/post/shiny-modules/
rstudioapi::addTheme("https://raw.githubusercontent.com/batpigandme/night-owlish/master/rstheme/night-owlish.rstheme", apply = TRUE)
https://serverfault.com/questions/11029/how-can-you-change-the-default-location-of-the-ssh-folder
https://github.com/rstudio/r2d3.

## D3 stuff here
https://towardsdatascience.com/getting-r-and-d3-js-to-play-nicely-in-r-markdown-
https://stackoverflow.com/questions/25819539/how-to-add-an-interactive-visualization-to-r-markdown
https://rstudio.github.io/r2d3/articles/introduction.html


